Supplemental Material for submission ``Do Objects in Real-World Images Have a Canonical Name?''

### 2019-05-20 papers/EMNLP2019/relwork.tex
small fixes in language in rel. work

\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
An important paradigm for experimental research here is picture naming, where human subjects are asked to say or write down the first name that comes to mind when looking at a given picture, typically a normed, black-and-white line drawing depicting a prototypical instance of a category on a white background \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
Subjects have been shown to reach very high agreement on this task, e.g.\ \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our annotation task is inspired by these picture naming studies, but uses real-world images with particular objects highlighted in them.
Recognition of instances (as opposed to categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}. Object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}. 
In L\&V,  deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly. For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for e.g. people are missing.

\paragraph{Work on Hierarchical Object Categorization} is not only interested in visual object representations but also in principles underlying the organization of these object categories. 
For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the hierarchical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy. 
%This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}. 
While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single correct or canonical category (that does have relations to other categories). 
This view has been criticized by more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple taxonomies at the same time \cite{ross1999food,SHAFTO20111}. A prominent example for this \textit{cross-classification} are food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
To the best of our knowledge, this phenomenon has not received any attention in recent corpus-based work on L\&V.
Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.

>>>>

\paragraph{Work on Visual Object Recognition} studies and models object representations in the human visual system, cf.\ \cite{regan2000human,rossion2004revisiting}. 
An important paradigm for experimental research here is picture naming, where human subjects are asked to say or write down the first name that comes to mind when looking at a given picture, typically a normed, black-and-white line drawing depicting a prototypical instance of a category on a white background \cite{snodgrass}, see Figure \ref{fig:picture_naming}.
Subjects have been shown to reach very high agreement on this task, \cite{rossion2004revisiting}, and the resulting naming norm data is useful for studying various cognitive processes \cite{humphreys1988cascade}.
Our annotation task is inspired by picture naming, but uses real-world images with particular objects highlighted in them.
Recognition of instances (as opposed to prototypes or categories) in images has also been the focus of computer vision, where state-of-the-art systems are now able to classify of real-world objects into thousands of different categories, e.g.\  \newcite{googlenet}. 
Current object recognition benchmarks use object labels (and images) from the ImageNet \cite{imagenet_cvpr09} taxonomy, but typically frame the task as a multi-label classification problem where taxonomic relations between labels are not considered \cite{ILSVRC15}. 
In L\&V,  deep object recognition systems are widely used for feature extraction, whereas the object labeling itself can often not be used directly. For instance, many labels in the ILSVRC15 challenge correspond to very specific breeds of animals, whereas other common categories  for e.g. people are missing.

\paragraph{Work on Hierarchical Object Categorization} goes beyond visual representations of isolated categories but looks at the principles underlying the organization of object categories. 
For instance, seminal work on prototypes by Rosch \cite{rosch1976basic} has emphasized the taxonomical organization of categories and found that humans tend to conceptualize objects at a basic or medium level of abstraction in this taxonomy. 
%This suggests that object names typically exhibit a preferred level of specificity, which \citet{jolicoeur1984pictures} called the \textbf{entry-level}, e.g, \refexp{bird}, \refexp{car}), as opposed to more generic (e.g., \refexp{animal}, \refexp{vehicle}) or specific categories (e.g., \refexp{sparrow}, \refexp{convertible}).Less prototypical members of basic-level categories have been found to be identified with sub-level categories (e.g., a \cat{penguin} is typically called a \refexp{penguin} and not a \refexp{bird}) \cite{jolicoeur1984pictures}. 
Hierarchical or "granularity-aware" approaches to visual object recognition have aimed at exploiting the rich taxonomical structure underlying object labels \cite{Deng:2012,frome2013,deng2014large,wang2014poodle,peterson2018learning}. 
While this work goes beyond the simplistic modeling assumption that categories are just unrelated labels, the main objective here is still to predict a single, canonical category (that does have relations to other categories). 
This view has been criticized in more recent work on concept organization, which found that many objects that we frequently interact with in our daily lifes are part of multiple category systems at the same time \cite{ross1999food,SHAFTO20111}. A prominent example for this \textit{cross-classification} are food categories which can be taxonomy-based (e.g.\  \refexp{meat, vegetable}) or script-based (e.g.\  \refexp{breakfast, snack}).
To the best of our knowledge, this phenomenon has not received any attention in recent corpus-based work on L\&V.
Our results, however, suggest that cross-classification occurs very frequently when naming objects in real-world images.
